R Tools for Observations, Receptors and Footprints (rtorf)

### 2025-09-17 README.Rmd
addding legacy code to be refactored in the future. Keeping here for tracking

>>>>

### Note about legacy code.

I received the task of reformat legacy code used to read PARTICLE.DAT and generate
NetCDF. This code is really old and since STILT and other have permissive licenses,
it is here, however, some code is not exported to NAMESPACE. 
A future version of rtorf, will have a new design for the legacy code,
a modern and efficient approach, keeping the essential tasks.
